2D or not 2D, that is the question\\ {\footnotesize Should we be looking for epistasis in GWAS?}

### 2012-06-21 eQTL_2D/presentation/icqg4/icqg4_hemani.tex
icgq4 talk finished

\title[Epistasis in GWAS]{2D or not 2D, that is the question\\
{\footnotesize Should we be looking for epistasis in GWAS?}}
\author{Gibran Hemani}
\institute{The Roslin Institute, University of Edinburgh \\
\vspace{.3cm}
Diamantina Institute \\and \\
Queensland Brain Institute,\\
University of Queensland}
\date{}
\begin{document}

@@

\begin{frame}{Very preliminary results}
\begin{itemize}
\item Is there much non-additive variance?
\item 71 probes have significant eQTLs after filtering for:
\begin{itemize}
\item Threshold of 16.5
\item Additive variance $\leq$ 60\% of total genetic variance
\item Relatively common SNPs (must have samples for all 9 genotype classes)
\item No LD between interacting SNPs
\end{itemize}
\item Total of 140 significant independent loci
\end{itemize}
\end{frame}

@@

{\tiny
PhD Funding:
\begin{itemize}
\item The Roslin Institute
\item University of Edinburgh
\item Biosciences KTN
\item Monsanto / Newsham Choice Genetics
\end{itemize}
PhD Supervisors:
\begin{itemize}
\item Chris Haley
\item Sara Knott
\item John Woolliams
\end{itemize}
Important people:
\begin{itemize}
\item Ricardo Pong-Wong
\item Athanasios Theocharidis
\item Wenhua Wei
\end{itemize}
Compute resources
\begin{itemize}
\item ECDF - {\tt eddie}
\item Daresbury Labs - {\tt cseht}
\item IVEC - {\tt fornax}
\end{itemize}
}

@@

\begin{itemize}
\item Peter Visscher
\item Naomi Wray
\item Joseph Powell
\item Jian Yang
\item Allan Mcrae
\item Anita Goldinger
\item Hong Lee
\item Anna Vinkhuyzen
\item Guo-Bo Chen
\item Beben Benyamin
\item Zong Zhang
\item Enda Byrne
\item Marie-Jo Brion
\item Sven Stringer
\end{itemize}
}

@@

>>>>

\title[Epistasis in GWAS]{2D or not 2D, that is the question\\
{\footnotesize Should we be looking for epistasis in GWAS?}}
\author{Gibran Hemani, Sara Knott, Joseph Powell, Naomi Wray, Peter Visscher, Chris Haley}
\institute{The Roslin Institute, University of Edinburgh \\
\vspace{.3cm}
Diamantina Institute \\and \\
Queensland Brain Institute,\\
University of Queensland}
\date{}
\begin{document}

@@

\begin{frame}{Very preliminary results}
\begin{itemize}
\item Is there much non-additive variance?
\item 71 probes have significant eQTLs after filtering for:
\begin{itemize}
\item Threshold of 16.5
\item Additive variance $\leq$ 60\% of total genetic variance
\item Relatively common SNPs (must have samples for all 9 genotype classes)
\item No LD between interacting SNPs
\end{itemize}
\item Number of significant epistatic pairs: \textbf{140}
\end{itemize}
\end{frame}

@@

{\tiny
PhD Funding:
\begin{itemize}
\item The Roslin Institute
\item University of Edinburgh
\item Biosciences KTN
\item Monsanto / Newsham Choice Genetics
\end{itemize}
PhD Supervisors:
\begin{itemize}
\item Chris Haley
\item Sara Knott
\item John Woolliams
\end{itemize}
Important people:
\begin{itemize}
\item Ricardo Pong-Wong
\item Athanasios Theocharidis
\item Wenhua Wei
\end{itemize}
Compute resources
\begin{itemize}
\item ECDF - {\tt eddie}
\item Daresbury Labs - {\tt cseht}
\item IVEC - {\tt fornax}
\item QBI cluster
\end{itemize}
}

@@

\begin{itemize}
\item Peter Visscher
\item Naomi Wray
\item Joseph Powell
\item Jian Yang
\item Allan Mcrae
\item Anita Goldinger
\item Hong Lee
\item Anna Vinkhuyzen
\item Guo-Bo Chen
\item Beben Benyamin
\item Zong Zhang
\item Enda Byrne
\item Marie-Jo Brion
\item Sven Stringer
\item Visit us at www.complextraitgenomics.com
\end{itemize}
}

@@

\begin{frame}{Narrow-sense heritability}
\begin{figure}
% \begin{minipage}[c]{0.38\textwidth}
\includegraphics[width=6cm]{visscher2008_heritabiliy.jpg} \\
{\tiny Visscher, 2008}
\end{figure}
\begin{itemize}
\item Fitness related traits have lower heritabilites
\item Additive variance appears to be maintained under selection
\item Response to selection is lower than expected for fitness related traits
\end{itemize}
\end{frame}
